---
title: "Extract Model Outputs"
author: "Mohamed Albirair"
date: "9/17/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE, results = 'hold', warning = FALSE,
                      message = FALSE, error = FALSE)

pacman::p_load(tidyverse)
```

# Simple Linear Regression Models

Below is a function that extracts simple linear models outputs (or `glm()` models with `family = "gaussian"` specification).

```{r linear model ouptut, results='hide'}

lmmod <- lm(mpg ~ cyl + gear + hp,
            data = mtcars)

lmOutputExtract <- function(mod){
            lmOutput <- data.frame(coefficients(summary(mod))[, c(1, 4)], confint(mod)) %>%
                  dplyr::select(1, 3, 4, 2) %>% round(., 3) %>%
                  `colnames<-`(c("Coefficient", "LCL", "UCL", "P-value")) %>%
                  mutate(`P-value` = case_when(`P-value` < 0.001 ~ "<0.001*",
                                               `P-value` < 0.05 ~ paste0(`P-value`,"*"),
                                               `P-value` >= 0.05 ~ as.character(`P-value`)))
            print(lmOutput)}
 
linearOutput <- lmOutputExtract(lmmod)
```

```{r linear modeul output formatted}
linearOuptut %>%
      knitr::kable("latex", caption = "Linear regression model output") %>%
      kableExtra::kable_styling(latex_options = c("striped", "HOLD_position"), fixed_thead = T)
```

# Simple Logistic Regression Models

The function below can be used for simple logistic and poisson regression models as well as other models were the associations are on the multiplicative scale (i.e., that assess relationships on the log scale)

```{r q1b, results='hide'}
logitmod <- glm(factor(am) ~ mpg + cyl + hp,
                data = mtcars,
                family = binomial(link = "logit"))

logitOutputExtract <- function(mod){
      logitOutput <- data.frame(exp(coefficients(summary(mod)))[, 1],
                                   coefficients(summary(mod))[, 4],
                                   exp(confint(mod))) %>%
            dplyr::select(1, 3, 4, 2) %>% round(., 3) %>%
            `colnames<-`(c("Coefficient", "LCL", "UCL", "P-value")) %>%
            mutate(`P-value` = case_when(`P-value` < 0.001 ~ "<0.001*",
                                         `P-value` < 0.05 ~ paste0(`P-value`,"*"),
                                         `P-value` >= 0.05 ~ as.character(`P-value`)))
      print(logitOutput)
}
logitOutput <- logitOutputExtract(logitmod)
```

```{r q1bOutput}
hw04mod1logitOuptut %>%
      knitr::kable("latex", caption = "Logistic regression model output") %>%
      kableExtra::kable_styling(latex_options = c("striped", "HOLD_position"), fixed_thead = T)
```

