---
title: "Extract Model Outputs"
author: "Mohamed Albirair"
date: "9/17/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE, results = 'hold', warning = FALSE,
                      message = FALSE, error = FALSE)

pacman::p_load(tidyverse)
```

# Simple Linear Regression Models

Below is a function that extracts simple linear models outputs (or `glm()` models with `family = "gaussian"` specification).

```{r linear model ouptut, results='hide'}

lmmod <- lm(mpg ~ cyl + gear + hp,
            data = mtcars)

caschools <- read_csv("https://vincentarelbundock.github.io/Rdatasets/csv/AER/CASchools.csv") %>%
      # Data and dictionary are from the link: https://vincentarelbundock.github.io/Rdatasets/datasets.html
      mutate(stratio = students / teachers,
             score = (math + read) / 2)

lmmod <- lm(score ~ stratio + lunch + computer + expenditure, data = caschools)

lmOutputExtract <- function(mod){
            lmOutput <- data.frame(coefficients(summary(mod))[, c(1, 4)], confint(mod)) %>%
                  dplyr::select(1, 3, 4, 2) %>% round(., 3) %>%
                  `colnames<-`(c("Coefficient", "LCL", "UCL", "P-value")) %>%
                  mutate(`P-value` = case_when(`P-value` < 0.001 ~ "<0.001*",
                                               `P-value` < 0.05 ~ paste0(`P-value`,"*"),
                                               `P-value` >= 0.05 ~ as.character(`P-value`)))
            print(lmOutput)
}
 
linearOutput <- lmOutputExtract(lmmod)
```

```{r linear modeul output formatted}
linearOutput %>%
      pander::pander(., caption = "Linear regression model output", style = "rmarkdown")
```

# Simple Logistic Regression Models

The function below can be used for simple logistic and poisson regression models as well as other models were the associations are on the multiplicative scale (i.e., that assess relationships on the log scale)

```{r q1b, results='hide'}
# Using variables from the same data set as above (with no theoretical foundation)
logitmod <- glm(factor(grades) ~ stratio + lunch + computer + expenditure,
                # factor is needed because the binary output MUST have an inherent ranking
                # i.e., needs to understand which one of the 2 values would be the reference.
                # The factor() commands takes care of that
                family = "binomial", # or, more specifically, binomial(link = "logit")
                data = caschools)

logitOutputExtract <- function(mod){
      logitOutput <- data.frame(exp(coefficients(summary(mod)))[, 1],
                                   coefficients(summary(mod))[, 4],
                                   exp(confint(mod))) %>%
            dplyr::select(1, 3, 4, 2) %>% round(., 3) %>%
            `colnames<-`(c("Coefficient", "LCL", "UCL", "P-value")) %>%
            mutate(`P-value` = case_when(`P-value` < 0.001 ~ "<0.001*",
                                         `P-value` < 0.05 ~ paste0(`P-value`,"*"),
                                         `P-value` >= 0.05 ~ as.character(`P-value`)))
      print(logitOutput)
}

logitOutput <- logitOutputExtract(logitmod)
```

```{r q1bOutput}
logitOutput %>%
      pander::pander(., caption = "Linear regression model output", style = "rmarkdown")
```

